Viscous Transport in Eroding Porous Media

### 2019-06-13 docs/transport/erosion_transport.tex
add new figs in transport paper
redo figs in transport paper

{\color{red}
In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
$\tau$ at two neighboring tracers 
and draw the trajectories of neighboring tracers in 
Fig.~\ref{fig:Eroding20tort_traj}
if the difference of $\tau$ at the neighboring tracers is large. 
From Fig.~\ref{fig:Eroding20tort_traj},
 we are able to tell the neighboring trajectories will be very 
different if they are separated by bodies. In Fig.~\ref{fig:Eroding20tort_traj}
we collect the 10 largest difference of $\tau$ at the neighboring tracers and 
draw the pair of trajectories in the same color. For each pair of trajectories, 
they are splitted by the body at the left side of the body, then
one of them goes up and the other one goes down along the body 
until they rejoin with each other at the right side of body.  
Furthermore, the pair trajectories could be splitted by more than one body, 
for example in Fig.~\ref{fig:Eroding20tort_traj} the toppest red pair trajectories 
are splitted by three close bodies. 
}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/diff_tort}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies.
(a) The 
x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=6.2281
\times 10^{-4}$ at equal spreading tracers on the cross section x = -1. 
(b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
\end{figure}

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top20}
\caption{\label{fig:Eroding20tort_traj} The largest 10 difference of 
local tortuosity $\tau$ at two neighboring tracers in
 20 nearly touching bodies eroding. The same color of a pair of trajectories 
means they are from two neighboring tracers.}
\end{figure}

>>>>

{\color{red}
In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
$\tau$ at two neighboring tracers 
and draw the trajectories of neighboring tracers in 
Fig.~\ref{fig:Eroding20tort_traj}
if the difference of $\tau$ at the neighboring tracers is large. 
From Fig.~\ref{fig:Eroding20tort_traj},
 we are able to tell the neighboring trajectories will be very 
different if they are separated by bodies. In Fig.~\ref{fig:Eroding20tort_traj}
we collect the 10 largest difference of $\tau$ at the neighboring tracers and 
draw the pair of trajectories in the same color. For each pair of trajectories, 
they are splitted by the body at the left side of the body, then
one of them goes up and the other one goes down along the body 
until they rejoin with each other at the right side of body.  
Furthermore, the pair trajectories could be splitted by more than one body, 
for example in Fig.~\ref{fig:Eroding20tort_traj} the toppest red pair trajectories 
are splitted by two close bodies. (?)
}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc20_268}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local20_268}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/diff_tort20_268}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax20_268}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies.
(a) The 
x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=6.2281
\times 10^{-4}$ at equal spreading tracers on the cross section x = -1. 
(b) The local tortuosity $\tau(y)$ on the cross section x = -1. 
(c) The difference of $\tau(y)$ at two neighboring tracers on the cross section x = -1.
(d) The ratio of the minimum to maximum speeds along the trajectories of tracers.}
\end{figure}

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top10_268}
\caption{\label{fig:Eroding20tort_traj} The largest 10 difference of 
local tortuosity $\tau$ at two neighboring tracers in
 20 nearly touching bodies eroding. The same color of a pair of trajectories 
means they are from two neighboring tracers.}
\end{figure}
